Meaning of simple rules in investment strategies of algorithmic trading

### 2013-10-29 Article/book/FormatProposal/tewi-paper-template.tex
book format proposal - latex tests

>>>>

\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for CHFJPY}
 \begin{center}
 \begin{tabular}{|l|l|l|l|l|}
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
S1s & 14.85 & 5.68 & Group of MA & 4945\\
\hline \end{tabular}
 \end{center}
 \end{table}
\begin{minipage}{\linewidth}
\includegraphics[width=0.49\textwidth]{images/chfjpyA.eps}
\subcaption{Profit - pyA}
\begin{minipage}{\linewidth}
\includegraphics[width=0.49\textwidth]{images/chfjpyB.eps}
\subcaption{Profit - pyB}
\begin{minipage}{\linewidth}
\includegraphics[width=0.49\textwidth]{images/chfjpyC.eps}
\subcaption{Profit - pyC}
\begin{minipage}{\linewidth}
\includegraphics[width=0.49\textwidth]{images/chfjpyD.eps}
\subcaption{Profit - pyD}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/chfjpyD.eps}
\subcaption{Profit - S1s}
\caption{CHFJPY market results}
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for EURJPY}
 \begin{center}
 \begin{tabular}{|l|l|l|l|l|}
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
S1s & 14.85 & 5.68 & Group of MA & 4945\\
\hline \end{tabular}
 \end{center}
 \end{table}
\begin{minipage}{\linewidth}
\includegraphics[width=0.49\textwidth]{images/eurjpyA.eps}
\subcaption{Profit - pyA}
\begin{minipage}{\linewidth}
\includegraphics[width=0.49\textwidth]{images/eurjpyB.eps}
\subcaption{Profit - pyB}
\begin{minipage}{\linewidth}
\includegraphics[width=0.49\textwidth]{images/eurjpyC.eps}
\subcaption{Profit - pyC}
\begin{minipage}{\linewidth}
\includegraphics[width=0.49\textwidth]{images/eurjpyD.eps}
\subcaption{Profit - pyD}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/eurjpyD.eps}
\subcaption{Profit - pyD}
\caption{EURJPY market results}
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for FUS500}
 \begin{center}
 \begin{tabular}{|l|l|l|l|l|}
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
S1s & 14.85 & 5.68 & Group of MA & 4945\\
\hline \end{tabular}
 \end{center}
 \end{table}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/fus500A.eps}
\subcaption{Profit - 00A}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/fus500B.eps}
\subcaption{Profit - 00B}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/fus500C.eps}
\subcaption{Profit - 00C}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/fus500D.eps}
\subcaption{Profit - 00D}
\caption{FUS500 market results}
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for GBPCHF}
 \begin{center}
 \begin{tabular}{|l|l|l|l|l|}
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
S1s & 14.85 & 5.68 & Group of MA & 4945\\
\hline \end{tabular}
 \end{center}
 \end{table}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/gbpchfA.eps}
\subcaption{Profit - hfA}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/gbpchfB.eps}
\subcaption{Profit - hfB}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/gbpchfC.eps}
\subcaption{Profit - hfC}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/gbpchfD.eps}
\subcaption{Profit - hfD}
\caption{GBPCHF market results}
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for SILVER}
 \begin{center}
 \begin{tabular}{|l|l|l|l|l|}
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
S1s & 14.85 & 5.68 & Group of MA & 4945\\
\hline \end{tabular}
 \end{center}
 \end{table}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/silverA.eps}
\subcaption{Profit - erA}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/silverB.eps}
\subcaption{Profit - erB}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/silverC.eps}
\subcaption{Profit - erC}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/silverD.eps}
\subcaption{Profit - erD}
\caption{SILVER market results}
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for CADCHF}
 \begin{center}
 \begin{tabular}{|l|l|l|l|l|}
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
S1s & 14.85 & 5.68 & Group of MA & 4945\\
\hline \end{tabular}
 \end{center}
 \end{table}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/cadchfS1a.eps}
\subcaption{Profit - S1a}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/cadchfS1b.eps}
\subcaption{Profit - S1b}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/cadchfS1c.eps}
\subcaption{Profit - S1c}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/cadchfS1d.eps}
\subcaption{Profit - S1d}
\includegraphics[width=0.82\textwidth]{images/cadchfS1s.eps}
\subcaption{Profit - S1s}
\caption{CADCHF market results}
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for FCOPPER}
 \begin{center}
 \begin{tabular}{|l|l|l|l|l|}
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
S1s & 14.85 & 5.68 & Group of MA & 4945\\
\hline \end{tabular}
 \end{center}
 \end{table}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/fcopperS1a.eps}
\subcaption{Profit - S1a}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/fcopperS1b.eps}
\subcaption{Profit - S1b}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/fcopperS1c.eps}
\subcaption{Profit - S1c}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/fcopperS1d.eps}
\subcaption{Profit - S1d}
\includegraphics[width=0.82\textwidth]{images/fcopperS1s.eps}
\subcaption{Profit - S1s}
\caption{FCOPPER market results}
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for FCORN}
 \begin{center}
 \begin{tabular}{|l|l|l|l|l|}
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
S1s & 14.85 & 5.68 & Group of MA & 4945\\
\hline \end{tabular}
 \end{center}
 \end{table}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/fcornS1a.eps}
\subcaption{Profit - S1a}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/fcornS1b.eps}
\subcaption{Profit - S1b}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/fcornS1c.eps}
\subcaption{Profit - S1c}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/fcornS1d.eps}
\subcaption{Profit - S1d}
\includegraphics[width=0.82\textwidth]{images/fcornS1s.eps}
\subcaption{Profit - S1s}
\caption{FCORN market results}
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for NZDJPY}
 \begin{center}
 \begin{tabular}{|l|l|l|l|l|}
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
S1s & 14.85 & 5.68 & Group of MA & 4945\\
\hline \end{tabular}
 \end{center}
 \end{table}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/nzdjpyS1a.eps}
\subcaption{Profit - S1a}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/nzdjpyS1b.eps}
\subcaption{Profit - S1b}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/nzdjpyS1c.eps}
\subcaption{Profit - S1c}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/nzdjpyS1d.eps}
\subcaption{Profit - S1d}
\includegraphics[width=0.82\textwidth]{images/nzdjpyS1s.eps}
\subcaption{Profit - S1s}
\caption{NZDJPY market results}
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for USDCAD}
 \begin{center}
 \begin{tabular}{|l|l|l|l|l|}
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline
S1a & 17.19 & 8.24 & 18 & 2693\\ \hline
S1b & -9.80 & -0.74 & 54 & 2665\\ \hline
S1c & 5.65 & 2.06 & 54 & 2280\\ \hline
S1d & 1.87 & 0.61 & 18 & 2287\\ \hline
S1s & 14.85 & 5.68 & Group of MA & 4945\\
\hline \end{tabular}
 \end{center}
 \end{table}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/usdcadS1a.eps}
\subcaption{Profit - S1a}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/usdcadS1b.eps}
\subcaption{Profit - S1b}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/usdcadS1c.eps}
\subcaption{Profit - S1c}
\begin{minipage}{\linewidth}
\includegraphics[width=0.6\textwidth]{images/usdcadS1d.eps}
\subcaption{Profit - S1d}
\includegraphics[width=0.82\textwidth]{images/usdcadS1s.eps}
\subcaption{Profit - S1s}
\caption{USDCAD market results}
